The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2016-10-18 article.tex
Better title (HT to Tomáš)
Restored The.
More no-break spaces.

\title{Updated Chemistry Development Kit (CDK): atom typing, depiction, molecular formulas, and substructure searching}

\author[
   addressref={um},                                 % ORCID: 0000-0001-7542-0286
   %corref={aff1},
   %noteref={n1},
   email={egon.willighagen@maastrichtuniversity.nl}
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={nm},
   email={john.may@cantab.net}
]{\inits{JWM}\fnm{John W} \snm{Mayfield}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={azg},                                % ORCID: 0000-0001-9491-4134
   email={Lars.A.Carlsson@astrazeneca.com}
]{\inits{LC}\fnm{Lars}~\snm{Carlsson}}
% \author[
%    addressref={jena},
%    email={kai.duehrkop@uni-jena.de}
% ]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},                             % ORCID: 0000-0002-6940-3006
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},                             % ORCID: 0000-0002-4659-1446
   email={mrojas@qca.es}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas-Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris T} \snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

>>>>

\title{The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching}

\author[
   addressref={um},                                 % ORCID: 0000-0001-7542-0286
   %corref={aff1},
   %noteref={n1},
   email={egon.willighagen@maastrichtuniversity.nl}
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={nm},
   email={john.may@cantab.net}
]{\inits{JWM}\fnm{John W} \snm{Mayfield}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={azg},                                % ORCID: 0000-0001-9491-4134
   email={Lars.A.Carlsson@astrazeneca.com}
]{\inits{LC}\fnm{Lars}~\snm{Carlsson}}
% \author[
%    addressref={jena},
%    email={kai.duehrkop@uni-jena.de}
% ]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},                             % ORCID: 0000-0002-6940-3006
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},                             % ORCID: 0000-0002-4659-1446
   email={mrojas@qca.es}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas-Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris~T}~\snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}
